Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS

### 2023-08-29 paper/ms.tex
Update ms (JNW comments): methods
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex rotators (CRs)}:
    {\it Top:} Phase-folded TESS light curves of three CRs.  Each
    panel shows the average of the data accumulated over one month.
    Gray circles are raw 2-minute data; black circles are binned to
    300 points per cycle.  The period in hours is printed in the
    bottom right corner.  Left-to-right, the objects are LP 12-502
    (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
    425933644 (Sector~28).
    {\it Bottom:} Cartoon explanations for the phenomenon.  The dust
    clump scenario (left) and prominence scenario (right) both invoke
    magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

@@

Previous methods for finding CRs have included visually examining
stars in young clusters
\citep{2016AJ....152..114R,2017AJ....153..152S} and automatically
flagging rapid rotators with a large number of strong Fourier
harmonics \citep{2019ApJ...876..127Z}.  The latter approach still
requires visual vetting, since ``stars with strong Fourier harmonics''
is a designation that includes objects such as eclipsing binaries or
multiple stars blended into a single photometric aperture.  In this
work, we implemented a new search approach based on counting the
number of sharp local minima in phase-folded light curves, while also
using the Fourier approach.  We applied these two
search techniques independently.

\subsubsection{Counting dips}
\label{subsec:counting}

The dip counting technique aims to count sharp local minima in
phase-folded light curves.  CRs will preferably have at least three
such minima in order to be distinct from false positives such as
synchronized and spotted binaries (``RS CVn'' stars).

For our dip-counting pipeline, we began with the {\tt PDC\_SAP} flux
for each sector, removed non-zero quality flags, and normalized the
light curve to one by dividing out its median value.  We then
flattened the light curve using a 5-day sliding median filter, as
implemented in \texttt{wotan} \citep{2019AJ....158..143H}.  On the
resulting cleaned and flattened light curve, we ran a periodogram
search, opting for the \citet{1978ApJ...224..953S} phase dispersion
minimization (PDM) algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
$P$ below 2 days was identified, we reran the periodogram at a finer
grid to improve the accuracy of the period determination.

Once a star's period was identified, we binned the phased light curve
to 100 points per cycle.  To separate ``sharp'' local minima from
smooth spot-induced variability, we then iteratively fit
robust penalized splines to the wrapped phase-folded light curve,
excluding points more than two standard deviations away from the local
continuum \citep{2019AJ....158..143H}.  The maximum number of
equidistant spline knots per cycle is the parameter in this framework
that controlled the meaning of ``sharp'' --- we allowed at most 10
such knots per cycle, though for most stars fewer knots were preferred
based on cross-validation using an $\ell^2$-norm penalty.  An example
fit is shown in panel {\it (e)} of Figure~\ref{fig:vet}.

We then identified local minima in the resulting residual light curve
using the SciPy \texttt{find\_peaks} utility
\citep{2020NatMe..17..261V}, which is based on comparing adjacent
values in an array.  For a peak to be flagged as significant, we
required it to have a width of at least $0.02\,P$, and a height of at
least twice the point-to-point RMS.  This latter quantity is defined
as the 68$^{\rm th}$ percentile of the distribution of the residuals
from the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$
is the flux and $i$ is an index over time.

To identify local minima near the edges of the phased light curve,
which usually would cover phases $\phi \in [ 0,1 ]$, we performed the
entire procedure over a phase-folded light curve spanning $\phi \in
[-1,2 ]$, by duplicating and concatenating the ordinary phase-folded
light curve.  The free parameters we adopted throughout this analysis
procedure, for instance the maximum number of spline knots per cycle,
and how large and wide of a local minimum to consider a ``true dip'',
were chosen during testing based on their ability to correctly
re-identify a large fraction ($>$90\%) of previously known CRs, while also being
able to consistently reject common false positives such as rapidly
rotating spot-induced variability and typical eclipsing binaries.

Overall, for a star to proceed to manual examination, we required that
it have a peak PDM period below two days, and that it exhibited at
least three sharp local minima (as algorithmically reported) in at
least one observed TESS sector.

@@

We performed an independent search for strongly periodic phenomena
using a Fourier-based approach, following \citet{2019ApJ...876..127Z}
and \citet[][their Section~1.3]{2023MNRAS.524.4220P}.  Starting with
the {\tt PDC\_SAP} light curves, we normalized each light curve, and
then re-binned it into equal width 120-second bins to account for the
uneven spacing in the TESS data, as well as the data gap caused by
satellite downlink during each sector.  We then padded the data to
ensure that the light curve had a length that was a power of two, as
described by \citeauthor{2019ApJ...876..127Z}.  Taking the Fourier
transform of the padded light curve using {\tt numpy.fft},
we then searched for peaks with a significance of over 12-$\sigma$
within a set of 500 frequency bins.

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  In the sectors for which
we performed this analysis, we found that ``summary'' sheets were
generated for $\approx$10\% of the 20{,}000 120-second targets in a
given sector.  We then manually reviewed each summary sheet, and
visually labeled each star based on its morphology (including e.g.
eclipsing binary, CR, RS CVn, or cataclysmic variable).  CRs that
were observed in multiple sectors had their light curves stitched
together and analyzed for a more accurate period determination.

\subsubsection{Manual vetting}

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CRs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available in the online journal. {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc from \citet{2021A&A...649A...6G}.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

We assessed whether the objects found using the dip-counting
(Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) techniques were consistent with
expectations for CRs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CR if at least
one TESS sector showed what we viewed as the unambiguous signatures of
the class (short period; at least three dips or else otherwise
oddly-shaped dips; relative stability over a timescale of 30\,days).
We independently noted stars that we thought could be CRs, but that
were more ambiguous.

Broadly speaking, the most common false positive triggers for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and variability from neighboring,
off-target stars.  Typical false positive rates from our dip-counting
pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and
about 20\% being labeled either ``good'' or ``possible'' CRs.  The
Fourier analysis was not amenable to calculating a similar
false-positive rate, because it was implemented as a general
variability search; its results are also being used for analyses on
topics other than CRs.

@@

\paragraph{Ages}
We estimated the stellar ages by making probabilistic spatial and
kinematic associations between the CRs and known clusters in the
solar neighborhood.  For most stars in our sample, we did this using
BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the probability
that a given star belongs to one of 27 young clusters (or
``associations'') within 150\,pc of the Sun, by modeling the clusters
as multivariate Gaussians in 3-D position and 3-D velocity space.  We
used the Gaia DR2 sky positions, proper motions, and distances to
calculate the membership probabilities.  BANYAN\,$\Sigma$ in turn
analytically marginalizes over the radial velocity dimension.  The
probabilities returned by this procedure are qualitatively useful, but
should be assessed with caution due to the non-Gaussian nature of most
groups within the solar neighborhood \citep[see
e.g.][Figure~10]{2021ApJ...917...23K}.

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
within from \citet{2022AJ....163..121B}, and also searched the local
volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess; we similarly omitted WISE bands $W3$ and $W4$, but due to
reliability concerns.  \texttt{astroARIADNE} compares the measured
broadband flux measurements against pre-computed model grids, and by
default fits for six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V},
\log g, [{\rm Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  And finally, given our particular use-case,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

With the effective temperatures and stellar radii from the SED fit, we
then estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for anomalous M dwarf colors and sizes relative
to model predictions include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
t \}$ as
\begin{equation}
  d^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
in order to assign equal importance to each dimension.  The preferred
model mass is then one that minimizes this distance, and is quoted in
Table~\ref{tab:thetable}.  Uncertainties in the masses are propagated
forward from the statistical uncertainties in the radii, temperatures,
and ages.

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f3.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CRs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CRs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Objects are ordered such
      that sources with the most TESS data available are on top (see
      Section~\ref{sec:catalog}).  
      Each panel is labeled by
      the TIC identifier, the TESS sector number, the period in
      hours, and the three-bit binarity flag from Table~\ref{tab:thetable},
      which denotes Gaia DR3 \texttt{radial\_velocity\_error} outliers
      (bit 1), Gaia DR3 \texttt{ruwe} outliers (bit 2), and stars with
      secondary TESS periods (bit 3). 
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

>>>>

		\vspace{-0.65cm}
		\subfloat{
			\includegraphics[width=0.66\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.5cm}
	\caption{
		{\bf Complex rotators (CRs)}:
    {\it Top:} Phase-folded TESS light curves for three CRs.  Each
    panel shows the average of the data accumulated over one month,
    relative to the mean stellar brightness.
    Gray circles are raw 2-minute data; black circles are binned to
    300 points per cycle.  The period in hours is printed in the
    bottom right corner.  Left-to-right, the objects are LP 12-502
    (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
    425933644 (Sector~28).
    {\it Bottom:} Cartoon explanations for the phenomenon.  The dust
    clump scenario (left) and prominence scenario (right) both invoke
    magnetically-entrained corotating material.
	}
	\label{fig:f1}
\end{figure*}

@@

Prior to this study, most CRs have been found by visually examining
all the light curves of stars in young clusters
\citep{2016AJ....152..114R,2017AJ....153..152S,2023ApJ...945..114P},
or by flagging light curves with short periods and a large number of
strong Fourier harmonics for visual inspection
\citep{2019ApJ...876..127Z}.  In this work, we implemented a new
search approach based on counting the number of sharp local minima in
phase-folded light curves, while also using the Fourier approach.  We
applied these two search techniques independently.

%FIXME TODO LEFT OFF HERE
\subsubsection{Counting dips}
\label{subsec:counting}

The dip counting technique aims to count sharp local minima in
phase-folded light curves.  The most remarkable CRs often show three
or more dips per cycle, which distinguishes them from other types of
variables such as synchronized and spotted binaries (RS CVn stars).

For our dip-counting pipeline, we began with the {\tt PDC\_SAP} light
curves for each sector, removed non-zero quality flags, and normalized
the light curve by dividing out its median value.  We then flattened
the light curve using a 5-day sliding median filter, as implemented in
\texttt{wotan} \citep{2019AJ....158..143H}.  We computed a periodogram
of the resulting cleaned and flattened light curve, opting for the
\citet{1978ApJ...224..953S} phase dispersion minimization (PDM)
algorithm implemented in \texttt{astrobase}
\citep{2021zndo...1011188B} due to its shape agnosticism.  If a period
$P$ below 2 days was identified, we reran the periodogram at a finer
grid to improve the accuracy of the period determination.

Once a star's period was identified, we binned the phased light curve
to 100 points per cycle.  To separate sharp local minima from smooth
spot-induced variability, we then iteratively fit robust penalized
splines to the wrapped phase-folded light curve, excluding points more
than two standard deviations away from the local continuum
\citep{2019AJ....158..143H}.  The wrapping procedure is discussed
below.  In this fitting framework, the maximum number of equidistant
spline knots per cycle is the parameter that controlled the meaning of
``sharp'' --- we allowed at most 10 such knots per cycle, though for
most stars fewer knots were preferred based on cross-validation using
an $\ell^2$-norm penalty.  An example fit is shown in panel {\it (e)}
of Figure~\ref{fig:vet}.

We then identified local minima in the resulting residual light curve
using the SciPy \texttt{find\_peaks} utility
\citep{2020NatMe..17..261V}, which is based on comparing adjacent
values in an array.  For a peak to be flagged as significant, we
required it to have a width of at least $0.02\,P$, and a height of at
least twice the noise level.  The noise level was defined
as the 68$^{\rm th}$ percentile of the distribution of the residuals
from the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$
is the flux and $i$ is an index over time.
In panel {\it (e)} of Figure~\ref{fig:vet}, automatically-identified
local minima are shown with the gray triangles.

Wrapping is necessary to eliminate edge
effects when fitting the light curve and when identifying local minima
in the residuals.  A phased light curve would usually cover phases
$\phi \in [ 0,1 ]$.  We instead performed the entire preceding
procedure over a phase-folded light curve spanning $\phi \in [-1,2 ]$,
which was created by duplicating and concatenating the ordinary
phase-folded light curve.  The free parameters we adopted throughout
this analysis -- for instance the maximum number of spline knots per
cycle, and the height and depth criteria for dips -- were chosen
during testing based on the desire to correctly re-identify a large
fraction ($>$90\%) of previously known CRs, while also being able to
consistently reject common false positives such as rapidly rotating
spot-induced variability and typical eclipsing binaries.

In short, CR candidates were identified by requiring a peak PDM period
below two days and the presence of at least three sharp local minima,
based on at least one sector of the TESS 120-second data. Candidates
were then inspected visually as described in
Section~\ref{subsec:visual}.

@@

We performed an independent search using a Fourier-based approach,
following \citet{2019ApJ...876..127Z} and \citet[][their
Section~1.3]{2023MNRAS.524.4220P}.  Starting with the {\tt PDC\_SAP}
light curves, we normalized each light curve, and then re-binned it
into equal width 120-second bins to account for the uneven spacing in
the TESS data, as well as the data gap caused by satellite downlink
during each sector.  We then padded the data to ensure that the light
curve had a length that was a power of two, as described by
\citeauthor{2019ApJ...876..127Z}.  After taking the Fourier transform
of the padded light curve using {\tt numpy.fft}, we searched for peaks
with a significance exceeding 12-$\sigma$ within a set of 500
frequency bins.

If a peak of such significance was found, we generated a ``summary
sheet'' with information about the star, its full and folded light
curves, Fourier transform, potential contaminating stars, and
information about these contaminating stars.  Summary sheets were
generated for $\approx$10\% of the 20{,}000 120-second targets in each
sector.  We reviewed each summary sheet and tried to classify each
light curve based on visual inspection of its morphology (with
categories including eclipsing binary, CR, RS CVn, and cataclysmic
variable). Whenever a CR was identified, the light curves from
multiple sectors were stitched together and analyzed jointly, for a
more accurate period determination.

\subsubsection{Manual vetting}
\label{subsec:visual}

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CRs}.  The complete figure
			set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}
			is available in the online journal. {\bf For internal collaboration review:
				\url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

We assessed whether the objects found using the dip-counting
(Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) techniques were consistent with
expectations for CRs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CR if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise
    oddly-shaped dips.
  %
  \item Dip phases (mostly) repeat over $\approx$30\,day sector duration.
\end{itemize}
\vspace{-2pt}
We also noted ''possible'' CRs for which the classification was more
ambiguous, and ``false positives'' that are definitely not CRs.  The
most common false positives for both the Fourier and dip-counting
techniques were eclipsing binaries, ordinary spotted rapid rotators,
and complex light curves due to multiple stars contributing to the
photometric aperture.  Our dip-counting pipeline flagged
\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
subsequently labeled either good or possible CRs.  From the Fourier
pipeline, $\approx$0.5\% of stars that passed the 12-$\sigma$ peak
threshold were eventually classified as CRs.  This is because the
Fourier pipeline was implemented as a general variability search; its
results are also being used for analyses on topics other than CRs.

@@

\paragraph{Ages}
We estimated the stellar ages by making probabilistic spatial and
kinematic associations between the CRs and known clusters in the solar
neighborhood.  For most stars in our sample, we did this using
BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the probability
that a given star belongs to one of 27 young clusters (or
``associations'') within 150\,pc of the Sun, by modeling the clusters
as multivariate Gaussian distributions in 3-D position and 3-D
velocity space.  We used the Gaia DR2 sky positions, proper motions,
and distances to calculate the membership probabilities.
BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial
velocity dimension.  The probabilities returned by this procedure are
qualitatively useful, but should be interpreted with caution because
the assumption of Gaussian distributions is questionable for most
groups within the solar neighborhood \citep[see
e.g.][Figure~10]{2021ApJ...917...23K}.

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
provided by \citet{2022AJ....163..121B}, and also searched the local
volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}}

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

With the effective temperatures and stellar radii from the SED fit, we
estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for the disagreement between observed and
theoretical M dwarf colors and sizes include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G} and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
model PARSEC grid-point $\{ T_{\rm eff}, M_\star, t \}$ via
\begin{equation}
  \Delta^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
where the division by the uncertainties helps to assign equal
importance to each dimension.  The mass reported in
Table~\ref{tab:thetable} is the model mass that minimizes the
distance.  The reported uncertainties in the masses are based on
propagating the statistical uncertainties in the radii, temperatures,
and ages.

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f3.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CRs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CRs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Objects are ordered such
      that sources with the most TESS data available are on top (see
      Section~\ref{sec:catalog}).  Zero phase is chosen to correspond
      to minimum light.  Each panel is labeled by the TIC identifier,
      the TESS sector number, the period in hours, and the three-bit
      binarity flag from Table~\ref{tab:thetable}, which denotes Gaia
      DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
      \texttt{ruwe} outliers (bit 2), and stars with secondary TESS
      periods (bit 3). 
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}
